### 2015-01-26 paper_30_measure.tex
minor changes

\subsection{INDICATORS}
Performance indicators can be crucial measurements
within any business setting, and an SDO is no exception. Many
SDOs struggle to determine the correct indicators to track and
how to track them.  
The differences between the indicators will be explored and
possible measures for each indicator in an SDO will be
presented.  The 4 different types of indicators are:
\begin{description}
  \item[RI (Result Indicator)] - what has been done
  \item[KRI (Key Result Indicator)] - how you have done
  \item[PI (Performance Indicator)] - what to do
  \item[KPI (Key Performance Indicator)] - what to do to dramatically increase performance
\end{description}

>>>>

\subsection{INDICATORS}
Indicators can be crucial measurements
within any business setting, and an SDO is no exception. Determining
the correct indicators for an organization can
be difficult.  Software development organizations
The differences between the indicators will be explored and
possible measures for each indicator in an SDO will be
presented.  The 4 different types of indicators are:
\begin{description}
  \item[RI (Result Indicator)] - what has been done
  \item[KRI (Key Result Indicator)] - how you have done
  \item[PI (Performance Indicator)] - what to do
  \item[KPI (Key Performance Indicator)] - what to do to dramatically increase performance
\end{description}
